%-------------------------
% Resume in Latex
% Author : Nicolás Tallar
% Website: https://github.com/ntallar/cv
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\labelitemii}{$\circ$}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\setlength{\footskip}{5pt}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\input{resume-commands.tex}


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}l}
  \textbf{\Large Nicol\'as Tallar}  & \faEnvelopeSquare \ \href{mailto:nicolastallar@gmail.com}{nicolastallar@gmail.com} \\
                                    & \faGithub \ \href{https://github.com/ntallar}{https://github.com/ntallar} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheadingTitleWithoutDesc
      {Universidad de Buenos Aires}{CABA, Argentina}
      {BS+Master in Computer Science;  GPA: 9.38}{Jan. 2012 -- sometime in 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheadingTitle
      {Globant}{CABA, Argentina}
      {Tech Leader \& Typescript Dev}{Mar 2023 - now}
      {Led development of various services for a marketplace application}
      \resumeItemListStart
        \resumeItemTechStack{Typescript, NestJS, Azure, SQL}
        \resumeItem{Extensive integration to the Azure ecosystem: Blob Storage (using SAS), Queue Storage, Azure functions}
      \resumeItemListEnd

    \resumeSubheadingSubtitleWithoutDesc
      {Tech Leader \& Solidity Dev at \href{https://gitlab.com/atixlabs-oss/agua}{Agua project}}{Dec 2022 - Mar 2023}
      %{Designed Solidity Smart Contracts, integrating with flows implemented on a NodeJS application.}
      \resumeItemListStart
        \resumeItemTechStack{Solidity, Javascript, Hardhat, OpenZeppelin}
      \resumeItemListEnd

    \resumeSubheadingSubtitle
      {Tech Leader \& Kotlin Dev}{Dec 2021 - Dec 2022}
      {Led development of part of the microservices for a gaming application: a Kotlin and a Java microservice, both built on the Spring Boot framework.}
      \resumeItemListStart
        \resumeItemTechStack{Kotlin (libraries: Arrow), Java, Solidity, Spring Boot, Hardhat, AWS (DynamoDB, S3)}
        \resumeItem{Market Research of Wallet and NFT products and protocols}
        \resumeItem{Design \& coordination for the integration of the implemented microservices with the others}
      \resumeItemListEnd

    \resumeSubheadingTitle
      {Atix Labs}{CABA, Argentina}
      {Tech Leader \& Scala Dev at \href{https://github.com/input-output-hk/mantis}{Mantis project}}{Sep 2020 - Jan 2021}
      {Led modernization of a Ethereum Classic client, a Scala protocol implementation modeled with Akka actors.}
      \resumeItemListStart
        \resumeItemTechStack{Scala (libraries: Akka, Cats, Monix), NoSQL (RocksDB)}
        \resumeItemWithDetails
          {Design \& implementation of a protocol change to Ethereum Classic}
          {\href{https://ecips.ethereumclassic.org/ECIPs/ecip-1098}{a proto-treasury system.}}
      \resumeItemListEnd

    \resumeSubheadingSubtitle
      {Squad Captain \& Scala Dev}{Sep 2018 - Sep 2020; Jan 2021 - Ago 2021}
      {Led development of a subteam for a project implementing a new cryptocurrency, through a layered Scala application integrated to Solidity contracts.}
      \resumeItemListStart
        \resumeItemTechStack{Scala (libraries: Akka, Cats, Monix), Solidity, NoSQL (RocksDB)}
        \resumeItem{Strict functional programming}
        \resumeItemWithDetails
          {Research-oriented development}
          {in close communication with a dedicated research team in charge of creating the protocol changes that our team implemented.}
        \resumeItem{Design \& implementation of the synchronization process between nodes of the cryptocurrency}
      \resumeItemListEnd

    \resumeSubheadingSubtitle
      {Haskell Dev at \href{https://github.com/input-output-hk/project-icarus-importer}{Yoroi project}}{Jan 2018 - Sep 2018}
      {Developed a Haskell integration to the Cardano Blockchain, that exposed events happing on it by exporting them to a SQL database. Helped with the Javascript Backend and Frontend as consumers of the produced database.}
      \resumeItemListStart
        \resumeItemTechStack{Haskell, SQL}
        \resumeItem{Designed integration with Cardano node}
      \resumeItemListEnd

    \resumeSubheadingSubtitle
      {Scala Dev at \href{https://github.com/input-output-hk/mantis}{Mantis project}}{Dec 2016 - Jan 2018}
      {Developed a Ethereum and Ethereum Classic client, a Scala protocol implementation modeled with Akka actors.}
      \resumeItemListStart
        \resumeItemTechStack{Scala (Akka actors), NoSQL (LevelDB and RocksDB)}
        \resumeItemWithDetails
          {Network Compatible with Ethereum and Ethereum Classic}
          {basing protocol implementation on the Ethereum paper and other of its implementations.}
        \resumeItemWithDetails
          {Open Source project}
          {with periodic status updates to the community.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
    \resumeSubItemWithDetails{Languages}
      {Scala (w/libraries: Akka, Cats, Monix), Kotlin (w/libraries: Arrow), Typescript, Haskell}
      % Solidity
    \resumeSubItemWithDetails{Technologies}
      {Spring Boot, NestJS, NoSQL, SQL, AWS (DynamoDB, S3), Azure (functions, Blob, Queue), Docker}
      % Hardhat
 \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects \& Courses}
  \resumeSubHeadingListStart
    \resumeSubItemWithDetails
      {IOHK Haskell \& Cryptocurrency Course}
      {3 month course focused on Haskell development}
    \resumeSubItem{Thesis on Simulations of Selfish Mining attack on the Bitcoin network}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}