% Education section
\def \secEducation{Education}
\def \degree{BS+Master in Computer Science;  GPA: 9.36}
\def \degreeDates{Jan. 2012 -- Aug. 2023}

% Experience section
\def \secExperience{Experience}

\def \marketplacePosition{Tech Leader \& Typescript Dev}
\def \marketplaceDates{Mar 2023 - now}
\def \marketplacePosDetails{Led development of various services for a marketplace application}
\def \marketplaceTechStack{Typescript, NestJS, Azure, SQL}
\def \marketplaceItemi{Extensive integration to the Azure ecosystem}
\def \marketplaceItemiDetails{Blob Storage (using SAS), Queue Storage, Azure functions}
\def \marketplaceItemii{Design \& coordination for the integration of all services of the application}

\def \aguaPosition{Tech Leader \& Solidity Dev at \href{https://gitlab.com/atixlabs-oss/agua}{Agua project}}
\def \aguaDates{Dec 2022 - Mar 2023}
\def \aguaTechStack{Solidity, Javascript, Hardhat, OpenZeppelin}

\def \gamingappPosition{Tech Leader \& Kotlin Dev}
\def \gamingappDates{Dec 2021 - Dec 2022}
\def \gamingappPosDetails{Led development of various microservices for a gaming application: a Kotlin and a Java microservice, both built on the Spring Boot framework.}
\def \gamingappTechStack{Kotlin (libraries: Arrow), Java, Spring Boot, AWS (DynamoDB, S3)}
                         % Solidity, Hardhat
\def \gamingappItemi{Market Research of Wallet and NFT products and protocols}

\def \mantisiiPosition{Tech Leader \& Scala Dev at \href{https://github.com/input-output-hk/mantis}{Mantis project}}
\def \mantisiiDates{Sep 2020 - Jan 2021}
\def \mantisiiPosDetails{Led modernization of a Ethereum Classic client: a Scala protocol implementation modeled with Akka actors.}
\def \mantisiiTechStack{Scala (libraries: Akka, Cats, Monix), NoSQL (RocksDB)}
\def \mantisiiItemi{Design \& implementation of a protocol change to Ethereum Classic}
\def \mantisiiItemiDetails{\href{https://ecips.ethereumclassic.org/ECIPs/ecip-1098}{a proto-treasury system.}}

\def \cryptoPosition{Squad Captain \& Scala Dev}
\def \cryptoDates{Sep 2018 - Sep 2020; Jan 2021 - Aug 2021}
\def \cryptoPosDetails{Led development of a subteam for a project implementing a new cryptocurrency, through a layered Scala application integrated to Solidity contracts.}
\def \cryptoTechStack{Scala (libraries: Akka, Cats, Monix), Solidity, NoSQL (RocksDB)}
\def \cryptoItemi{Strict functional programming}
\def \cryptoItemii{Research-oriented development}
\def \cryptoItemiiDetails{in close communication with a dedicated research team in charge of creating the protocol changes that our team implemented.}
\def \cryptoItemiii{Design \& implementation of the synchronization process between nodes of the cryptocurrency}

\def \yoroiPosition{Haskell Dev at \href{https://github.com/input-output-hk/project-icarus-importer}{Yoroi project}}
\def \yoroiDates{Jan 2018 - Sep 2018}
\def \yoroiPosDetails{Developed a Haskell integration to the Cardano Blockchain, that exposed events happing on it by exporting them to a SQL database. Helped with the Javascript Backend and Frontend as consumers of the produced database.}
\def \yoroiTechStack{Haskell, SQL}
\def \yoroiItemi{Designed integration with Cardano network}

\def \mantisiPosition{Scala Dev at \href{https://github.com/input-output-hk/mantis}{Mantis project}}
\def \mantisiDates{Dec 2016 - Jan 2018}
\def \mantisiPosDetails{Developed a Ethereum and Ethereum Classic client: a Scala protocol implementation modeled with Akka actors.}
\def \mantisiTechStack{Scala (Akka actors), NoSQL (LevelDB and RocksDB)}
\def \mantisiItemi{Network Compatible with Ethereum and Ethereum Classic}
\def \mantisiItemiDetails{basing protocol implementation on the Ethereum paper and other of its implementations.}
\def \mantisiItemii{Open Source project}
\def \mantisiItemiiDetails{with periodic status updates to the community.}

% Programming skills section
\def \secProgrammingSkills{Programming Skills}
\def \subsecProgrammingLang{Languages}
\def \programmingLang{Scala (w/libraries: Akka, Cats, Monix), Kotlin (w/libraries: Arrow), Typescript, Haskell}
     % Solidity
\def \subsecKnownTech{Technologies}
\def \knownTech{Spring Boot, NestJS, NoSQL, SQL, AWS (DynamoDB, S3), Azure (functions, Blob, Queue)}
     % Hardhat, Docker

% Projects and courses section
\def \secProjAndcCurses{Projects \& Courses}
\def \haskellCourse{IOHK Haskell \& Cryptocurrency Course}
\def \haskellCourseDetails{3 month course focused on Haskell development}
\def \thesis{Thesis on high-scale simulations of Selfish Mining attack on the Bitcoin network}